Automatic Matching of Bullet Lands

### 2016-04-15 revision/response.Rmd

5. The authors should discuss their work in the context of Nicholas Petraco’s work as well as other ongoing research endeavors in impression and pattern evidence. See https://www.ncjrs.gov/pdffiles1/nij/grants/239048.pdf The alignment method should have been compared with a standard method- See Patraco’s NIJ report for a couple of examples. As presented the novel component of the paper is the ``twicing" for grooves combined with a loess fit to the remove curves from bullet images. I am not sure this is the authors intention. It would be interesting to compare this method with some of the classical methods from functional data analysis used for curve registration.

6. page 7- figure 4- What exactly are you bootstrapping? It is unclear in the paper whether you are bootstrapping residual or bullets or something else entirely. Please clarify.

7. There should have been a comparison of different classification methods to show that the random forest is reasonable.

***I am not quite sure what a 'reasonable' classification method is supposed to mean. Shouldn't a classification method be judged by its success in predicting the outcome? 
Apart from that, random forests are based on decision trees, which are an extremely flexible tool for classification, that can deal with quantitative and categorical types of variables and, in the implementation we used, also deal with some missing values (which was not needed in the data here).***

@@

8. On the random forest classifier- are the prior probabilities being estimated from the cross comparisons described on page 15? What exactly are the prior probabilities used in the random forest?

***No data-based adjustment was made to the prior probabilities, i.e. prior probabilities of 50:50 for matches/non-matches were used.
HH: what does the reviewer mean by cross-comparison? On page 15 we discuss some results from matching based on CMS.***

@@

9. Equal Error Rates on the ROC curves would be a helpful metric as well as the AUC.

***included***

10. Would it be possible to stress the classification system by only using part of the profile? Such as would occur when a partial bullet is recovered? By stressing the random forest you would be able to compare it to other classifiers.

***Yes, it would be possible to stress the classification system by using only parts of the profile, but a systematic evaluation of this by far exceeds the scope of this paper.***

@@

11. What is the standard error of the error rates presented for the matching algorithms? The number of cross comparisons gives false impression the standard errors the when presenting the results.

***HH: I'm sure I am misunderstanding the comment, but I don't know how to answer this question. The standard error of a rate in (0,1) would be sqrt(p*(1-p)). So because p is small the square root is going to be still pretty small. 
We are presenting out of bag error rates for the random forest - maybe we need to explain what out-of bag means in more detail?***

### 2016-04-15 imaging-paper.Rnw
light grey shading for figure 5

\begin{figure}[hbtp]
\centering
\includegraphics[width=.65\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}3D view of the manually adjusted side-by-side comparison of bullet~1-5 and bullet 2-1 after removing the curvature.}
\end{figure}

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[width=.65\columnwidth]{images/matchup-rgl-copy.png}
\caption{\label{fig:manualmatch-rgl}3D view of the manually adjusted side-by-side comparison of bullet~1-5 and bullet 2-1 after removing the curvature. \hh{Bullet 2-1 is shaded light grey in the background.}}
\end{figure}
